The Practical Application of Computerised Multistage Tests

### 2021-03-04 article.Rmd
Ability to load test designs from file

```{r setup, include=FALSE}
library(knitr)
library(tidyverse)

@@

In this example we'll change the number of items per module; keeping the total number of items administered constant, but changing the relative number of items as follows:

| Design | Stage 1 | Stage 2 | Stage 3 | Total |
| ------ | ------: | ------: | ------: | ----: |
| 1      | 12      | 8       | 10      | 30    |
| 2      | 12      | 10      | 8       | 30    |
| 3      | 10      | 12      | 8       | 30    |
| 4      | 10      | 8       | 12      | 30    |
| 5      | 8       | 10      | 12      | 30    |
| 6      | 8       | 12      | 10      | 30    |

We define the `mstDesign()` function to generate the set of test designs we want to investigate. This function varies the number of items for each module by stage and can be repeatedly applied to the set of designs in the `stages` list. It effectively generates variants of the test design presented above in \@ref(module difficulties) for 3-stage designs.

```{r MST designs}
mstDesign <- function(stage, difficulties) {
  matrixN <- stage[1] + (2 * stage[2]) + (4 * stage[3])
  modules <- matrix(0, matrixN, 7)
  moduleA <- stage[1]
  moduleB <- moduleA+stage[2]
  moduleC <- moduleB+stage[2]
  moduleD <- moduleC+stage[3]
  moduleE <- moduleD+stage[3]
  moduleF <- moduleE+stage[3]
  moduleG <- moduleF+stage[3]

  modules[1:moduleA, 1] <- 1
  modules[moduleA+1:stage[2], 2] <- 1
  modules[moduleB+1:stage[2], 3] <- 1
  modules[moduleC+1:stage[3], 4] <- 1  
  modules[moduleD+1:stage[3], 5] <- 1
  modules[moduleE+1:stage[3], 6] <- 1
  modules[moduleF+1:stage[3], 7] <- 1

  itembank <- rbind(genDichoMatrix(stage[1], model = "1PL", bPrior = c("norm", 0.0, 1)),
                    genDichoMatrix(stage[2], model = "1PL", bPrior = c("norm", -2.0, 1)),
                    genDichoMatrix(stage[2], model = "1PL", bPrior = c("norm", 2.0, 1)),
                    genDichoMatrix(stage[3], model = "1PL", bPrior = c("norm", -3.0, 1)),
                    genDichoMatrix(stage[3], model = "1PL", bPrior = c("norm", -1.0, 1)),
                    genDichoMatrix(stage[3], model = "1PL", bPrior = c("norm", 1.0, 1)),
                    genDichoMatrix(stage[3], model = "1PL", bPrior = c("norm", 3.0, 1)))
  itembank <- as.matrix(itembank)

@@

stages <- list(c(12,8,10), c(12,10,8), c(10,12,8),
               c(10,8,12), c(8,10,12), c(8,12,10))
testDesigns <- lapply(stages, mstDesign)
```

>>>>

```{r setup, include=FALSE}
library(knitr)
library(tidyverse)
library(janitor)

@@

In this example we'll change the mean difficulties of the modules as well as the number of items per module; keeping the total number of items administered constant, but changing the relative number of items as follows:

```{r}
designParams <- read_csv('mst-designs.csv', skip = 1) %>%
  clean_names() %>%
  dplyr::select(-design, -total)

print(designParams)
```

We define the `mstDesign()` function to generate the set of test designs we want to investigate. This function varies the number of items for each module by stage and can be repeatedly applied to a set of designs which we load in from a CSV file. The `mstDesign()` function effectively generates variants of the test design presented above in \@ref(module difficulties) for 3-stage designs.

```{r MST designs}
mstDesign <- function(stage1, stage2, stage3,
                      module_a, module_b, module_c, module_d, module_e, module_f, module_g) {
  matrixN <- stage1 + (2 * stage2) + (4 * stage3)
  modules <- matrix(0, matrixN, 7)
  moduleA_items <- stage1
  moduleB_items <- moduleA_items + stage2
  moduleC_items <- moduleB_items + stage2
  moduleD_items <- moduleC_items + stage3
  moduleE_items <- moduleD_items + stage3
  moduleF_items <- moduleE_items + stage3
  moduleG_items <- moduleF_items + stage3

  modules[1:moduleA_items, 1] <- 1
  modules[moduleA_items+1:stage2, 2] <- 1
  modules[moduleB_items+1:stage2, 3] <- 1
  modules[moduleC_items+1:stage3, 4] <- 1
  modules[moduleD_items+1:stage3, 5] <- 1
  modules[moduleE_items+1:stage3, 6] <- 1
  modules[moduleF_items+1:stage3, 7] <- 1

  itembank <- rbind(genDichoMatrix(stage1, model = "1PL", bPrior = c("norm", module_a, 1)),
                    genDichoMatrix(stage2, model = "1PL", bPrior = c("norm", module_b, 1)),
                    genDichoMatrix(stage2, model = "1PL", bPrior = c("norm", module_c, 1)),
                    genDichoMatrix(stage3, model = "1PL", bPrior = c("norm", module_d, 1)),
                    genDichoMatrix(stage3, model = "1PL", bPrior = c("norm", module_e, 1)),
                    genDichoMatrix(stage3, model = "1PL", bPrior = c("norm", module_f, 1)),
                    genDichoMatrix(stage3, model = "1PL", bPrior = c("norm", module_g, 1)))
  itembank <- as.matrix(itembank)

@@

testDesigns <- pmap(designParams, mstDesign)
```
